---
title: "Data Product Week 4"
author: "Pierre Deceuninck"
date: "June 17, 2019"
output:
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(leaflet)
library(dplyr)

getColor <- function(quakes) {
  sapply(quakes$Magnitude, function(mag) {
  if(mag <= 7) {
    "green"
  } else if(mag <= 8) {
    "orange"
  } else {
    "red"
  } })
}

EarthquakeData <- read.csv(paste0(getwd(),"/data/database.csv"))
EarthquakeData <- EarthquakeData %>% 
    filter(Type=="Earthquake") %>% 
    mutate(Time=as.POSIXct(paste(Date,Time),format="%d/%m/%Y %H:%M:%S")) %>% 
    mutate(Date=as.Date(Date,format="%d/%m/%Y")) %>% 
    select(c("Date","Time","Depth","Magnitude","Magnitude.Type","Latitude","Longitude")) %>%
    filter(!is.na(Date)) %>%
    arrange(Time)


```
   
##Earthquake BDP4

Our shiny application will help professional or amateurs willing to get more information on earthquakes in a given area of the globe.

### Data selection

- Interactive geographical selection of an area of the globe
- Selection of the magnitude range of interest
- Selection of the time period of interest

### Selected data visualisation

- Frequency of eathquake by magnitude 
- Depth per earthquake magnitude
- Evolution of earquakes occurence magnitude over time

## The interactive earthquake map

```{r map, echo = FALSE, eval=TRUE, message=FALSE, out.width="100%"}
EarthquakeData %>% 
    leaflet() %>% 
    addTiles() %>%
    addCircleMarkers( 
               popup = paste0("<b>Date:</b> ", EarthquakeData$Date, " ", EarthquakeData$Time,
                              "<br><b>Magnitude:</b> ", EarthquakeData$Magnitude,
                              "<br><b>Depth:</b> ", EarthquakeData$Depth),
               weight = 1,
               radius = 10^(EarthquakeData$Magnitude/6),
               color = getColor(EarthquakeData)
               )
```

\newline

Click on a circle to get information / zoom in to select you area

## Map code

```{r map2, echo = TRUE, eval=FALSE}
EarthquakeData <- read.csv(paste0(getwd(),"/data/database.csv"))

EarthquakeData %>% 
    leaflet() %>% 
    addTiles() %>%
    addCircleMarkers( 
       popup = paste0("<b>Date:</b> ", 
         EarthquakeData$Date, " ", EarthquakeData$Time,
         "<br><b>Magnitude:</b> ", EarthquakeData$Magnitude,
         "<br><b>Depth:</b> ", EarthquakeData$Depth),
       weight = 1,
       radius = 10^(EarthquakeData$Magnitude/6),
       color = getColor(EarthquakeData)
    )
```

##All the info you want!!!

ShinyApp link:

- Documentation is on the fist tab (Help Page)
- Application is on the second (interactive map)

Git Source code: https://github.com/DeceuninckPierre/BDP_Week4

Have fun!!!
